%-----------------------------------------------------------------------------
% c0_outline.tex:
%     Thesis outline.         
%
%-----------------------------------------------------------------------------
\subsection*{Thesis Outline}
Titles marked with (*) are optional and will be added if I find the
extra time.

\begin{enumerate}
  
\item Introduction
  \begin{itemize}
  \item (opening) General intro to CFD and higher order methods
  \item Motivation: Current work on turbulent solvers, and the need for
    three-dimensional generalization
  \item Objective
  \item Outline
  \end{itemize}
  
\item Background
  \begin{itemize}
  \item The finite volume method
  \item k-exact reconstruction
  \item Flux evaluation methods
  \item Studied equations: Advection-Diffusion, Euler, RANS+SA
  \end{itemize}
  
\item Three dimensional mesh processing
  \begin{itemize}
  \item Control volume types: Introduce control volume types and their
    mapping to reference elements. (* Introduce the issue for
    reconstruction on pyramid elements)
  \item Mesh connectivity conversion: Convert face to cell
    connectivity as done in MeshCell3D preprocessing.
  \item Numerical integration: On generating quadrature points and
    their weights for general volume and surface integration.
  \item Creating curved anisotropic meshes: Methodology and results
    for solving the three dimensional elastic solid equations, from my
    MATH520 final project.
  \item Modified basis functions for reconstruction on highly
    anisotropic meshes: Introduce the $\xi, \zeta, \frac{1}{2}\xi^2,
    \xi\zeta, \frac{1}{2}\zeta^2\ldots$ reconstruction basis functions
    and cite Alireza's work. Also introduce the simple
    generalization with $\eta=z$ for the extruded meshes.
  \end{itemize}
  
\item Solution of the discretized system of equations
  \begin{itemize}
  \item Pseudo-transient continuation, Jacobian Matrix: Jacobian
    Assembly (*Matrix free method)
  \item Linear Solvers: Richardson, KSP (GMRES in particular)
  \item Preconditioning methods
    \begin{itemize}
    \item Single step preconditioning: Introduce ILU, Jacobi, Gauss-Sidel, Line
      Jacobi, Line Gauss Sidel on full order and first order Jacobians
    \item Find Lines of high DoF coupling  
    \item Hierarchical preconditioning: Chain linear solvers to
      improve performance
    \end{itemize}
  \end{itemize}
  
\item Numerical results
  \begin{itemize}
    \item Three dimensional advection-diffusion in a box: Show correct
      implementation of numerical quadrature by observing the correct
      convergence orders. Verify using exact solution.
    \item Subsonic inviscid flow around a sphere: Show the successful
      work of the preconditioner, and parallel scaling. Try to run up
      to 1M degrees of freedom. (*Implement matrix free method and
      compare storage.) Small verification by entropy norm.
    \item Subsonic two dimensional flow around multi element airfoil:
      Show the effectivity of the preconditioner for previously solved
      flows. No verification, maybe just show that the drag and lift
      are the same as before.
    \item Three dimensional turbulent flow around flat plate: Study
      scaling of the preconditioner. Full verification with NASA
      website. Study scaling.
      \item Three dimensional turbulent flow around extruded
        NACA0012: Demonstrate convergence. Report $C_f$ and $C_p$
        contours plus lift and drag coefficients (* Use curvilinear
        coordinates, and mixed meshes if possible).
  \end{itemize}
  
\item Conclusions

\end{enumerate}

%%% Local Variables:
%%% TeX-master: "diss"
%%% End:
\endinput
