%% The following is a directive for TeXShop to indicate the main file
%%!TEX root = diss.tex

%% https://www.grad.ubc.ca/current-students/dissertation-thesis-preparation/preliminary-pages
%% 
%% LAY SUMMARY Effective May 2017, all theses and dissertations must
%% include a lay summary.  The lay or public summary explains the key
%% goals and contributions of the research/scholarly work in terms that
%% can be understood by the general public. It must not exceed 150
%% words in length.

\chapter{Lay Summary}

Unstructured meshes are used widely in simulating flow over various objects in industry and government. The region near the surfaces of objects is particularly important during the simulation process because of the extreme non-linearity in the flow characteristics near the boundaries of objects. Hence, generating a well-discretized boundary layer mesh is key to superior flow simulation results. 3D mesh generation methodologies use a surface mesh as the starting point. Hence, the surface mesh plays an important role in the overall fluid flow simulation process.

A method to generate an advancing layer surface mesh is introduced in this paper. This method could be used to generate advancing-layer quad-dominant surface meshes with the required aspect ratio at sharp corners of the surface. 3D mesh generation procedures could use this mesh to produce advancing layer mesh or any other mesh. Example meshes are generated and shown to handle complex geometries.

%The lay or public summary explains the key goals and contributions of the research/scholarly work in terms that can be understood by the general public. It must not exceed 150 words in length.
